### 2015-03-20 paper_40_cri.tex
more grammatical fixes updates to lists in the appendix

    SDOs struggle to measure overall performance.  
    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
    number score to measure the performance of an SDO. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for an SDO.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements.  CRI is made to be easily 
    expandable to other elements if desired.

@@

    As long as those 5 features are met, the range of scores can be anything.  
    The range of $[-1,1]$ was chosen because it is easy to scale 
    to a different range such as $[-10,10]$ or $[-100,100]$.  
    Thus scaling can be applied to obtain values in any appropriate range. 
    The scaling factor is denoted with the variable $k$.  
    The scale must be the same
    for all 5 elements.

    \subsection{ELEMENTS OF CRI}
        Each of the 5 elements of CRI has its own set of data that needs to
        be collected and formula for calculating a score. 
        These five elements will be outlined in the next sections.

@@

            Another aspect of defects is severity levels.  A severity level indicates
            the importance of a defect that has been discovered.  Although an
            organization can choose whatever severity levels they choose, it is
            common practice to use 5 severity levels \cite{Raynus1999}.  The most 
            severe level for a defect is 1.  All other levels drop in severity 
            from that point. Table \ref{tab:severity} describes the 5 levels
            for defect severity.

@@

                Notice the data does not include a severity level.  The severity
                level should be handled before being stored.  A good technique is
                to count the defects based upon the weighting scheme
                in Table \ref{tab:severityweight} \cite{Raynus1999}. For
                example, finding 1 defect of severity level 5 will result
                in total count of 1.  However, finding 1 defect of severity
                level 2 will result in a total count of 15. This strategy helps
                to standardize the number of defects found.  An organization
                can alter the values of Table \ref{tab:severityweight} based 
                upon priorities or use a different technique if desired.  It
                is just important to get a standard, meaningful number for SIT defects,
                UAT defects, and PROD defects which manages severity appropriately.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statements
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets of customers need to be presented with a survey.  
                    In the case of CRI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

                    \item[Second] End-users will be surveyed for satisfaction. Obviously, the 
                    entire population cannot be surveyed, so a probability sample should 
                    be randomly created. Even then, bias will be present.  
                        \begin{itemize}
                            \item Not all users will respond.  This is because survey 
                                respondents tend to sit at the extremes of either 
                                satisfied or dissatisfied.  Thus the results will tend 
                                to indicate that separation. 
                            \item  Even with probability sampling it is possible to miss 
                                entire groups of population members. For example consider a 
                                banking application such as a savings account, a survey would 
                                most likely be presented online and it would have a coverage 
                                bias due the exclusion of savings account holders that 
                                do not bank online.
                            \item A selection bias can occur when some members of the 
                                population have a higher probability of inclusion in 
                                the sampling frame than others.  One example could be 
                                a user with multiple savings accounts.  The selection 
                                bias is typically easy to avoid if the bias is 
                                identified.  Weighting is a common solution for selection bias. 
                        \end{itemize}

@@

            \paragraph{SATISFACTION FORMULA}
                After collecting the necessary survey data from Table \ref{tab:satisfactiondata},
                calculating the score is rather straight forward.
                The scores for each question are averaged and then those
                values are averaged together.  If some survey questions
                are more important than others, the formula could be
                easily modified to include weighting.

@@

        \subsubsection{REQUIREMENTS}
            The requirements of an SDO are important. Requirements are desired 
            new features or enhancements to a software product.  It is important
            to know how many requirements
            were scheduled to be completed versus how many actually got completed. 
            They provide a measurement
            of the amount of work being completed. However, not all requirements
            are created equal.  Some requirements can be quickly and easily
            implemented while other requirements will take much longer.  It
            is often difficult to know the challenges ahead of time.  Due to
            this uncertainty, estimating
            the number of requirements a team can complete in a given time frame can
            be difficult. Thus, number of requirements is one way to measure 
            amount of work
            but there are others.  Here are 3 possible choices in descending
            order of preference.
            \begin{description}
                \item[Function Points] Function points measure the size of the
                    software functionality, not the size or time required
                    to implement the functionality \cite{Jensen2014}.  
                    If done properly,
                    function points will provide the most concise measurement
                    for amount of work being completed. 
                \item[Story Points] Story points, sometimes just referred to 
                    as stories, are broken down requirements that can be
                    completed in an Agile Sprint of 2 to 4 weeks.  A 
                    story is usually smaller, simpler, and more concise
                    that a plain requirement. 
                    Unfortunately, these only apply to an
                    SDO using the Agile methodology, specifically 
                    Scrum \cite{Ashmore2014}.
                \item[Requirements] These are just the requirements as
                    written by the users or business partners.  Each requirement
                    can vary greatly from another requirement.  Estimating
                    number of requirements can be a difficult if not impossible
                    task.  
            \end{description}

@@

            \paragraph{REQUIREMENTS FORMULA}
                The requirements formula is the percentage above or below the
                scheduled number of requirements. Requirements have a nice
                lower bound of 0 since negative requirements cannot be 
                completed\footnote{Theoritically, a negative requirement would
                be considered a defect.}.  Unfortunately, an upper bound
                does not exist.  The variability of requirements is not
                as large as the variability of the number of defects, so
                a simpler strategy can be used.  For requirements, a 
                multiplier $b$ will be used to find the upper bound. The
                number of scheduled requirements should be multiplied by
                $b$ to obtain the upper bound.  The value of $b$ should
                be determined by looking at the historical data to make sure
                no number of completed requirements will exceed $b$ times
                the number of scheduled requirements. An example will be shown
                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
                and 2. Also, the formula will be
                created to deal with a value going above the upper bound.

@@

        \subsubsection{OVERALL CRI SCORE}
            In order to accomplish the single number score that CRI requires,
            the 5 element scores must be combined. The combination of the scores
            is a weighted average.  The weights can be set based upon the 
            priority of the SDO.  Thus, the overall CRI score is calculated as below.

@@

            This weighted average allows for a score to be computed even when not
            all 5 elements are present. Just perform the weighted average with
            as many elements as present.  This technique allows CRI to implemented
            before data for all the elements has been collected.  Just begin
            to average elements as they become accessible.

    \subsection{CORRELATIONS IN CRI}
        It is possible that 2 or more of the 5 elements of CRI will be correlated.  This means that
        one of the elements can be predicted based upon the values of the other elements.  Although
        it is possible for correlation to occur between any of the elements, the satisfaction element
        is an obvious element which deserves attention due to the human involvement of the surveys. 
        If a schedule is missed or an important requirement dropped, that could have a large negative
        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
        possible that a decrease in quality could result in unexpected downtime which could have a
        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
        to missing functionality.

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sec:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        fluctuate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then the normal distribution can be used.
                See \cite{Saltelli2000} for more information on sensitivity analysis 
                in statistical modeling.
        \end{description}

@@

            Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
            areas  for software
            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how CRI addresses
            each focus area.  
            As can be seen, CRI clearly addresses the 3 main focus areas of software analytics.  CRI does not provide
            any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
            the focus areas.

@@

                User Experience & One of the 5 elements of CRI is satisfaction.  While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
                with the software product. Does it have the correct features? Are new features added in a timely manner? Of course, specific survey questions can be created to focus solely on a certain user experience. \\
                \myrowcolour%
                Quality & Again, one of the 5 elements specifically focuses on quality.  CRI provides a single number
                to measure quality.  Therefore, it is easy to track changes in quality over time.  CRI does not address
                how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
                Development Productivity & The combination of CRI elements, schedule and requirements, provide an 
                indication of development productivity. The schedule element measures the productivity
                related to estimated schedule. Similarly, the requirement element measures the amount of
                work actually being completed.  \\

@@

        \subsubsection{CRI VS. IMPORTANT QUESTIONS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to SDOs.

@@

        \subsubsection{CRI VS. BALANCED SCORECARD}
            Section \ref{sec:bsc} discusses the characteristics of the 
            balanced scorecard.  Table \ref{tab:bsc} presents a
            comparison of the characteristics of a balanced scorecard
            versus CRI.
            As the newer 2 characteristics of a balanced scorecard
            have only existed since 2010 and the adoption is limited,
            the comparison will only be against the original 4 balanced
            scorecard characteristics.

@@

        \subsubsection{CRI VS. PROJECT MANAGEMENT MEASUREMENT}
            Previously in Section \ref{sec:pm}, the project management
            measurement was presented.   Its greatest limitation is the lack of
            focus on the entire SDO.  Project management measurement says 
            nothing about the availability of the software infrastructure
            or the satisfaction of the users.  It is not near as comprehensive
            as either the balanced scorecard or CRI. Actually, CRI incorporates
            the 5 core measurements from project management.
            Plus, the process productivity
            number is less suitable for upper management and more
            suitable for project teams.  Although it does provide a single
            process productivity number, it is does not have the same focus
            as CRI.

>>>>

    SDOs struggle to measure overall performance.  
    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
    number score to measure the performance of an SDO. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following five 
    elements, which are actually KRIs,
    for an SDO.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements.  CRI is made to be easily 
    expandable to other elements if desired.

@@

    As long as those 5 features are met, the range of scores can be anything.  
    The range of $[-1,1]$ was chosen because it is easy to scale 
    to a different range such as $[-10,10]$ or $[-100,100]$.  
    Thus scaling can be applied to obtain values in any appropriate range. 
    The scaling factor is denoted with the variable $k$.  
    The scale must be the same
    for all five elements.

    \subsection{ELEMENTS OF CRI}
        Each of the five elements of CRI has its own set of data that needs to
        be collected and formula for calculating a score. 
        These five elements will be outlined in the next sections.

@@

            Another aspect of defects is severity levels.  A severity level indicates
            the importance of a defect that has been discovered.  Although an
            organization can choose whatever severity levels they choose, it is
            common practice to use five severity levels \cite{Raynus1999}.  The most 
            severe level for a defect is 1.  All other levels drop in severity 
            from that point. Table \ref{tab:severity} describes the five levels
            for defect severity.

@@

                Notice the data does not include a severity level.  The severity
                level should be handled before being stored.  A good technique is
                to count the defects based upon the weighting scheme
                in Table \ref{tab:severityweight} \cite{Raynus1999}. For
                example, finding one defect of severity level 5 will result
                in a total count of one.  However, finding one defect of severity
                level 2 will result in a total count of 15. This strategy helps
                to standardize the number of defects found.  An organization
                can alter the values of Table \ref{tab:severityweight} based 
                upon priorities or use a different technique if desired.  It
                is important to establish a standard, meaningful number for SIT defects,
                UAT defects, and PROD defects which manages severity appropriately.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statements
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets of customers need to be presented with a survey.  
                    In the case of CRI, there are two possible scenarios for sampling.  
                    \begin{enumerate}
                        \item When an SDO is part of a larger organization, there typically is
                        a small number of business partners that help to guide and 
                        direct the work performed by the SDO.  In this case, the business 
                        partners might be the the ones offering survey responses and they 
                        should all be willing to respond.  Thus, those business partners 
                        represent the entire population, and the surveys should result in 
                        a 100\% response rate which is technically a census.  
                        The only bias that will be present here is the bias of the business 
                        partners and sampling cannot control for that.

                        \item End-users will be surveyed for satisfaction. Obviously, the 
                        entire population cannot be surveyed, so a probability sample should 
                        be randomly created. Even then, bias will be present.  
                        \begin{itemize}
                            \item Not all users will respond.  This is because survey 
                                respondents tend to sit at the extremes of either 
                                satisfied or dissatisfied.  Thus the results will tend 
                                to indicate that separation. 
                            \item  Even with probability sampling it is possible to miss 
                                entire groups of population members. For example consider a 
                                banking application such as a savings account, a survey would 
                                most likely be presented online, and it would have a coverage 
                                bias due to the exclusion of savings account holders that 
                                do not bank online.
                            \item A selection bias can occur when some members of the 
                                population have a higher probability of inclusion in 
                                the sampling frame than others.  One example could be 
                                a user with multiple savings accounts.  The selection 
                                bias is typically easy to avoid if the bias is 
                                identified.  Weighting is a common solution for selection bias. 
                        \end{itemize}

                    \end{enumerate}

@@

            \paragraph{SATISFACTION FORMULA}
                After collecting the necessary survey data from Table \ref{tab:satisfactiondata},
                calculating the score is rather straightforward.
                The scores for each question are averaged and then those
                values are averaged together.  If some survey questions
                are more important than others, the formula could be
                easily modified to include weighting.

@@

        \subsubsection{REQUIREMENTS}
            The requirements of an SDO are important. Requirements are desired 
            new features or enhancements to a software product.  It is important
            to know how many requirements
            were scheduled to be completed versus how many actually got completed. 
            They provide a measurement
            of the amount of work being completed. However, not all requirements
            are created equal.  Some requirements can be quickly and easily
            implemented while other requirements will take much longer.  It
            is often difficult to know the challenges ahead of time.  Due to
            this uncertainty, estimating
            the number of requirements a team can complete in a given time frame can
            be difficult. Thus, the number of requirements is one way to measure 
            amount of work
            but there are others.  Here are three possible choices in descending
            order of preference.
            \begin{enumerate}
                \item \textbf{Function Points} - Function points measure the size of the
                    software functionality, not the size or time required
                    to implement the functionality \cite{Jensen2014}.  
                    If done properly,
                    function points will provide the most concise measurement
                    for amount of work being completed. 
                \item \textbf{Story Points} - Story points, sometimes just referred to 
                    as stories, are broken down requirements that can be
                    completed in an Agile Sprint of two to four weeks.  A 
                    story is usually smaller, simpler, and more concise
                    that a plain requirement. 
                    Unfortunately, these only apply to an
                    SDO using the Agile methodology, specifically 
                    Scrum \cite{Ashmore2014}.
                \item \textbf{Requirements} - These are just the requirements as
                    written by the users or business partners.  Each requirement
                    can vary greatly from another requirement.  Estimating
                    number of requirements can be a difficult if not impossible
                    task.  
            \end{enumerate}

@@

            \paragraph{REQUIREMENTS FORMULA}
                The requirements formula is the percentage above or below the
                scheduled number of requirements. Requirements have a nice
                lower bound of 0 since negative requirements cannot be 
                completed\footnote{Theoretically, a negative requirement would
                be considered a defect.}.  Unfortunately, an upper bound
                does not exist.  The variability of requirements is not
                as large as the variability of the number of defects, so
                a simpler strategy can be used.  For requirements, a 
                multiplier $b$ will be used to find the upper bound. The
                number of scheduled requirements should be multiplied by
                $b$ to obtain the upper bound.  The value of $b$ should
                be determined by looking at the historical data to make sure
                no number of completed requirements will exceed $b$ times
                the number of scheduled requirements. An example will be shown
                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
                and 2. Also, the formula will be
                created to deal with a value going above the upper bound.

@@

        \subsubsection{OVERALL CRI SCORE}
            In order to accomplish the single number score that CRI requires,
            the five element scores must be combined. The combination of the scores
            is a weighted average.  The weights can be set based upon the 
            priority of the SDO.  Thus, the overall CRI score is calculated as below.

@@

            This weighted average allows for a score to be computed even when not
            all five elements are present. Just perform the weighted average with
            as many elements as present.  This technique allows CRI to implemented
            before data for all the elements has been collected.  Just begin
            to average elements as they become accessible.

    \subsection{CORRELATIONS IN CRI}
        It is possible that two or more of the five elements of CRI will be correlated.  This means that
        one of the elements can be predicted based upon the values of the other elements.  Although
        it is possible for correlation to occur between any of the elements, the satisfaction element
        is an obvious element which deserves attention due to the human involvement of the surveys. 
        If a schedule is missed or an important requirement dropped, that could have a large negative
        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
        possible that a decrease in quality could result in unexpected downtime which could have a
        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
        to missing functionality.

@@

    \subsection{SENSITIVITY OF CRI}
    \label{sec:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        fluctuate drastically for similar values.  There are two possible techniques
        for testing the sensitivity of the formulas. 
        \begin{enumerate}
            \item Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then the normal distribution can be used.
                See \cite{Saltelli2000} for more information on sensitivity analysis 
                in statistical modeling.
        \end{enumerate}

@@

            Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
            areas  for software
            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how CRI addresses
            each focus area.  
            As can be seen, CRI clearly addresses the three main focus areas of software analytics.  CRI does not provide
            any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
            the focus areas.

@@

                User Experience & One of the five elements of CRI is satisfaction.  While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
                with the software product. Does it have the correct features? Are new features added in a timely manner? Of course, specific survey questions can be created to focus solely on a certain user experience. \\
                \myrowcolour%
                Quality & Again, one of the five elements specifically focuses on quality.  CRI provides a single number
                to measure quality.  Therefore, it is easy to track changes in quality over time.  CRI does not address
                how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
                Development Productivity & The combination of CRI elements, schedule and requirements, provide an 
                indication of development productivity. The schedule element measures the productivity
                related to estimated schedule. Similarly, the requirement element measures the amount of
                work actually being completed.  \\

@@

        \subsubsection{CRI VS. IMPORTANT QUESTIONS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions three important questions that
            software analytics must address.  Table \ref{tab:questions} presents the three questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to SDOs.

@@

        \subsubsection{CRI VS. BALANCED SCORECARD}
            Section \ref{sec:bsc} discusses the characteristics of the 
            balanced scorecard.  Table \ref{tab:bsc} presents a
            comparison of the characteristics of a balanced scorecard
            versus CRI.
            As the newer two characteristics of a balanced scorecard
            have only existed since 2010 and the adoption is limited,
            the comparison will only be against the original four balanced
            scorecard characteristics.

@@

        \subsubsection{CRI VS. PROJECT MANAGEMENT MEASUREMENT}
            Previously in Section \ref{sec:pm}, the project management
            measurement was presented.   Its greatest limitation is the lack of
            focus on the entire SDO.  Project management measurement says 
            nothing about the availability of the software infrastructure
            or the satisfaction of the users.  It is not near as comprehensive
            as either the balanced scorecard or CRI. Actually, CRI incorporates
            the five core measurements from project management.
            Plus, the process productivity
            number is less suitable for upper management and more
            suitable for project teams.  Although it does provide a single
            process productivity number, it is does not have the same focus
            as CRI.

### 2015-03-20 paper_50_sdlc-ae.tex
more grammatical fixes updates to lists in the appendix

    \subsection{DATABASE STRUCTURE}
        All the data necessary to compute CRI needs to be stored in a database.  This section will 
        lay out the structure of tables and relationships necessary to the store all the data
        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
        a programming language designed for managing data in relational database 
        management system.\nomenclature{SQL}{Structured Query Language}} 
        is written for an Oracle
        database, but the scripts can be modified to work with other databases
        such as: PostgreSQL, SQL Server, or MySQL.

@@

            The first set of tables that need to be created are tables
            to store the raw data that is collected.  These tables
            will match up with the necessary data for each of the 5 elements
            of CRI.  Figure \ref{fig:raw} provides a visual description
            of the tables that are needed.  The tables have no relationship
            with each other since they are raw data.  The primary goal of
            these tables is to store the raw data in a single location. The
            5 table names are:
            \begin{enumerate}
                \item QUALITY\_RAW
                \item AVAILABILITY\_RAW
                \item SATISFACTION\_RAW
                \item SCHEDULE\_RAW
                \item REQUIREMENTS\_RAW
            \end{enumerate}
            Notice these table names match with the 5 elements of CRI.

@@

            \begin{enumerate}
                \item QUALITY\_SCORE
                \item AVAILABILITY\_SCORE
                \item SATISFACTION\_SCORE
                \item SCHEDULE\_SCORE
                \item REQUIREMENTS\_SCORE
            \end{enumerate}
            Again, these table names match very closely with the 5 elements of CRI.

@@

        \subsubsection{FINAL SCORE TABLES FOR CRI}
            The final set of tables consists of only two tables.  
            \begin{enumerate}
                \item ELEMENT
                \item CRI\_SCORE
            \end{enumerate}
            The first
            table is the ELEMENT table.  It simply stores the CRI element 
            (Quality, Availability,Satisfaction,Schedule,Requirements,Overall) and 
            optional description. The second table is the CRI\_SCORE table.  
            It stores all the final element scores and the final overall CRI
            score.  It is related to the ELEMENT table.  Figure 
            \ref{fig:final_score_tables} provides a visual representation of the 
            relationship between the 2 tables.

>>>>

    \subsection{DATABASE STRUCTURE}
        All the data necessary to compute CRI needs to be stored in a database.  This section will 
        lay out the structure of tables and relationships necessary to store all the data
        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
        a programming language designed for managing data in relational database 
        management system.\nomenclature{SQL}{Structured Query Language}} 
        is written for an Oracle
        database, but the scripts can be modified to work with other databases
        such as: PostgreSQL, SQL Server, or MySQL.

@@

            The first set of tables that need to be created are tables
            to store the raw data that is collected.  These tables
            will match up with the necessary data for each of the five elements
            of CRI.  Figure \ref{fig:raw} provides a visual description
            of the tables that are needed.  The tables have no relationship
            with each other since they are raw data.  The primary goal of
            these tables is to store the raw data in a single location. The
            five table names are:
            \begin{enumerate}
                \item QUALITY\_RAW
                \item AVAILABILITY\_RAW
                \item SATISFACTION\_RAW
                \item SCHEDULE\_RAW
                \item REQUIREMENTS\_RAW
            \end{enumerate}
            Notice these table names match with the five elements of CRI.

@@

            \begin{enumerate}
                \item QUALITY\_SCORE
                \item AVAILABILITY\_SCORE
                \item SATISFACTION\_SCORE
                \item SCHEDULE\_SCORE
                \item REQUIREMENTS\_SCORE
            \end{enumerate}
            Again, these table names match very closely with the five elements of CRI.

@@

        \subsubsection{FINAL SCORE TABLES FOR CRI}
            The final set of tables consists of only two tables.  
            \begin{enumerate}
                \item ELEMENT
                \item CRI\_SCORE
            \end{enumerate}
            The first
            table is the ELEMENT table.  It simply stores the CRI element 
            (Quality, Availability, Satisfaction, Schedule, Requirements, Overall) and 
            an optional description. The second table is the CRI\_SCORE table.  
            It stores all the final element scores and the final overall CRI
            score.  It is related to the ELEMENT table.  Figure 
            \ref{fig:final_score_tables} provides a visual representation of the 
            relationship between the two tables.

### 2015-03-20 paper_70_case-study.tex
more grammatical fixes updates to lists in the appendix

    \subsection{QUALITY}
        The first step to dealing with the quality data is a quick
        analysis of the data.  Table \ref{tab:quality_desc} provides
        some descriptive statistics for the quality data.  Testing hours
        were not captured, but they are optional, so the analysis can 
        continue.

@@

    \subsection{SCHEDULE}
        Figure \ref{tab:schedule_desc} displays some descriptive statistics
        for the schedule data.  Since the data is mostly dates, the 
        descriptive statistics are limited, so extra values were
        added to the table after removing 4 outliers.  The new values
        in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
        Difference (Actual Finish - Schedule Finish), and 
        $\Delta$ ($\frac{\text{Difference}}{\text{Schedule Duration}}$ ).

@@

        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
        for the individual element scores.  No correlation appears
        to exist between any of the elements. The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.

>>>>

    \subsection{QUALITY}
        The first step for dealing with the quality data is a quick
        analysis of the data.  Table \ref{tab:quality_desc} provides
        some descriptive statistics for the quality data.  Testing hours
        were not captured, but they are optional, so the analysis can 
        continue.

@@

    \subsection{SCHEDULE}
        Figure \ref{tab:schedule_desc} displays some descriptive statistics
        for the schedule data.  Since the data is mostly dates, the 
        descriptive statistics are limited, so extra values were
        added to the table after removing four outliers.  The new values
        in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
        Difference (Actual Finish - Schedule Finish), and 
        $\Delta$ ($\frac{\text{Difference}}{\text{Schedule Duration}}$ ).

@@

        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
        for the individual element scores.  No correlation appears
        to exist between any of the elements. The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the four elements analyzed here remain independent.
